Value-Suppressing Uncertainty Maps

### 2017-09-14 paper/main.tex
Prepping for experiment one

\section{Introduction}
Uncertainty is an inescapable component of collecting, presenting, and using data. A common goal in the communication of uncertainty is promoting \emph{uncertainty-aware decisions}: the audience should be aware of the risks and rewards of certain decisions, modulate their confidence in their conclusions, and perhaps refrain from making a decision at all if there is too much uncertainty.  A way that designers can contribute to this goal is by ensuring that uncertainty information is \emph{well-integrated} with the rest of the data. That is, it should be difficult to discount or ignore the uncertainty in a dataset.

@@

\exampleFig
\section{Related Work}

@@

%TODO finalize factor levels, regenerate conditions figure
The experiment was a within-subjects design with 1 factor (encoding type) with $N$ levels. \figref{fig:conditions} shows examples of these factor levels. We had 8 replications for each level for the identification task, and 4 for the prediction task, for a total of $N$ stimuli for the first task, and $N$ for the second. We discuss the two experimental tasks in more detail in the following sections. Experimental materials, including data tables and stimuli generation code, are available at \url{URL-REMOVED-FOR-REVIEW}.

>>>>

\section{Introduction}
\exampleFig
Uncertainty is an inescapable component of collecting, presenting, and using data. A common goal in the communication of uncertainty is promoting \emph{uncertainty-aware decisions}: the audience should be aware of the risks and rewards of certain decisions, modulate their confidence in their conclusions, and perhaps refrain from making a decision at all if there is too much uncertainty.  A way that designers can contribute to this goal is by ensuring that uncertainty information is \emph{well-integrated} with the rest of the data. That is, it should be difficult to discount or ignore the uncertainty in a dataset.

@@

\section{Related Work}

@@

%TODO finalize factor levels, regenerate conditions figure
The experiment was a within-subjects design with 1 factor (encoding type) with $3$ levels. \figref{fig:conditions} shows examples of these factor levels. We had 8 replications for each level for the identification task, and 6 for the prediction task, for a total of $24$ stimuli for the first task, and $18$ for the second. We discuss the two experimental tasks in more detail in the following sections. Experimental materials, including data tables and stimuli generation code, are available at \url{URL-REMOVED-FOR-REVIEW}.
